Modelling last glacial cycle ice dynamics in the Alps

### 2017-01-25 articles/cycle/alps-cycle.tex
Develop methods (one sentence per paragraph).

\subsection{Ice sheet model set-up}
    Table~\ref{tab:params} -- Model parameters\\
    Fig.~\ref{fig:inputs} -- Climate and geothermal model inputs.\\
\subsection{Palaeo-climate forcing}
    Table~\ref{tab:records} -- Palaeo-climate records.\\
    Fig.~\ref{fig:timeseries} -- Low-resolution time series.\\
    Fig.~\ref{fig:footprints} -- Low-resolution ice cover.

>>>>

\subsection{Ice sheet model set-up}
    Table~\ref{tab:params} -- Model parameters\\
    Fig.~\ref{fig:inputs} -- Climate and geothermal model inputs.\\

    \begin{itemize}
    \item Ice dynamics are approximated by SSA+SIA.
    \item Ice temperature follows an enthalpy scheme.
    \item Bedrock temperature computed until 3\,km depth
    \item Temperature conditioned by geothermal flux (Fig.~\ref{fig:inputs}d).
    \item Basal sliding follwos a pseudo-plastic law.
    \item Yield stress is determined by a Mohr-Coulomb criterion.
    \item Till friction angle is constant.
    \item Till effective pressure relates to basal melt.
    \item Surface mass balance is computed by a PDD model.
    \item Modern T and P forcing from WorldClim (Fig.~\ref{fig:inputs}a and~b).
    \item Modern PDD SD forcing from ERA-Interim (Fig.~\ref{fig:inputs}c).
    \item SRTM topography with glaciers removed \citep{Huss.Farinotti.2012}.
    \end{itemize}

\subsection{Palaeo-climate forcing}
    Table~\ref{tab:records} -- Palaeo-climate records.\\
    Fig.~\ref{fig:timeseries} -- Low-resolution time series.\\
    Fig.~\ref{fig:footprints} -- Low-resolution ice cover.

    \begin{itemize}
    \item We conducted a 5/,km-resolution sensitivity study.
    \item We used three palaeo-temperature records (Table~\ref{tab:records}).
    \item All records scaled to fit the LGM extent (Table~\ref{tab:records}).
    \item All yield glaciation during MIS~4 and 2 (Fig.~\ref{fig:timeseries}).
    \item But otherwise very different results (Fig.~\ref{fig:timeseries}).
    \item Two yield two large MIS~4 ice extent (Fig.~\ref{fig:footprints}).
    \item Only EPICA yield realistic MIS~4 (Fig.~\ref{fig:footprints}).
    \end{itemize}
